\documentclass[10pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=.63in,bmargin=.63in,lmargin=.63in,rmargin=.63in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Kyle Brieden}
\newcommand{\addr}{10 Perimeter Park Dr. Apt 201, Atlanta, GA 30341}
\newcommand{\phone}{(979) 575-9459}
\newcommand{\email}{kyle@brieden.org}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
    \begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
    \vspace{4pt}
    {\fontfamily{phv}\selectfont\Large#1}
    \begin{itemize}
    \vspace{3pt}
}{
    \end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
    \vspace{-4pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
    \vspace{-1pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
    \vspace{-5pt}
    \item
    \textbf{#3} \\
    \textit{#1}---#2
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
    \resbigitem{#1}{#2}{#3}
    \vspace{-2pt}
    \begin{itemize}
}{
    \end{itemize}
}

\newenvironment{resedusec}[3]{
    \resbigitem{#1}{#2}{#3}
    \vspace{-2pt}
}


% This is a simple sublist
\newenvironment{reslist}[1]{
    \resitem{\textbf{#1}}
    \vspace{-5pt}
    \begin{itemize}
}{
    \end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Objective}
%
%   \begin{ressubsec}{Seeking a challenging and rewarding position with the Critical Accounts team at Big Company.}
%   \end{ressubsec}
%
%\end{ressection}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

    \resitem{\textbf{Operating Systems:} Linux (Debian, Ubuntu, ArchLinux, CentOS), familiarity with current Windows and Mac OSX versions.}

    \begin{reslist}{Orchestration Technologies:}
        \ressubitem{Ansible, Salt Stack, Puppet}
    \end{reslist}

    \begin{reslist}{Linux Technologies:}
        \ressubitem{Apache, Nginx, MySQL, PHP-FPM, git, NFS, OpenLDAP, OpenSSL, OpenVPN, OpenFTP, OpenSSH, Postfix, Dovecot}
    \end{reslist}

    \begin{reslist}{Networking Technologies:}
        \ressubitem{TCP/IP, Hourglass Internet Model, OSI Model, Layer 2 and 3 hardware and software (including Cisco IOS).}
    \end{reslist}

    \begin{reslist}{Cloud Technologies}
		\ressubitem{Cloud Providers:  AWS, Digital Ocean, Rackspace}
        \ressubitem{Hypervisors:  Xen Project, VMware, KVM}
    \end{reslist}

    \begin{reslist}{Languages:}

        \ressubitem{Able to work in Bash, Python, PHP, HTML, \LaTeX\ }

    \end{reslist}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{ressection}{Certifications}
%    \begin{reslist}{Red Hat Certified Engineer}
%        \ressubitem{RHEL 6}
%        \ressubitem{12 July 2013}
%        \ressubitem{Certificate Number: 130-101-207}
%    \end{reslist}
%\end{ressection}
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

    \begin{ressubsec}{Macy's Systems \& Technology}{Johns Creek, GA}{Analyst 2 - Linux Automation: September 2016-Present}
        \ressubitem{Responsible for developing automation for internal customers.}
        \ressubitem{Provide day to day operational support for Macy's infrastructure at large.}
        \ressubitem{Linux Automation}
    \end{ressubsec}

    \begin{ressubsec}{Kickboard For Schools}{New Orleans, LA}{DevOps Engineer: June 2016-September 2016}
        \ressubitem{Responsible for developing foundation for growth of platform.}
        \ressubitem{Provide team with Systems Engineering experience and knowledge.}
        \ressubitem{DevOps Engineer - Full Time - Remote - Contract}
    \end{ressubsec}

    \begin{ressubsec}{WP Engine}{Austin, TX}{Operations Engineer: November 2014-April 2016}
        \ressubitem{Responsible for farm-wide monitoring and first response.  Assisting Systems Engineering team.}
        \ressubitem{Farm maintenance, rolling out updates, and assisting support staff when needed}
        \ressubitem{Operations Center - Third Shift}
    \end{ressubsec}

    \begin{ressubsec}{WP Engine}{Austin, TX}{Customer Support - Level 3: June 2014-November 2014}
        \ressubitem{System focused, but also worked with customer custom code as well.}
        \ressubitem{Emphasis on mentoring and training junior support techs and assisting management with day to day items.}
        \ressubitem{Third Shift Customer Support Team}
    \end{ressubsec}

    \begin{ressubsec}{Rackspace}{San Antonio, TX}{Linux Administrator II: January 2014-June 2014}
        \ressubitem{Linux Subject Matter Expert (SME) for Rackspace's most strategic accounts}
        \ressubitem{Critial Accounts - Enterprise Support}
    \end{ressubsec}

    \begin{ressubsec}{Rackspace}{San Antonio, TX}{Linux Adminstrator I: December 2012-January2014}
        \ressubitem{Provided chat and phone support, as well as ticket work for SMB customers from \$15 per month up to \$10,000 per month.}
        \ressubitem{Managed Cloud - SMB}
    \end{ressubsec}
    \begin{ressubsec}{TAMU Telecommunications Academy}{College Station, TX}{Student Worker-BVCNet Admin: June 2011-December 2011}
        \ressubitem{Developed, planned, and began deploying multiple public access computer labs around Bryan and College Station, TX.}
        \ressubitem{Developed a roaming profile-like system so patrons could log in at any lab and have their own desktop.}
        \ressubitem{Semester long position.}
    \end{ressubsec}

    \begin{ressubsec}{TAMU Cisco Lab}{College Station, TX}{Student Worker-Testing Assistant: September 2010-May 2011}
        \ressubitem{Tested networking products for Cisco Systems under professor Sejun Song at TAMU.}
        \ressubitem{Semester long position.}
    \end{ressubsec}

\end{ressection}
\begin{ressection}{Education}
    \begin{resedusec}{Texas A\&M University} {College Station, TX} {Telecommunications Engineering Technology}
    \end{resedusec}
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

    \resitem{Member of the Corps of Cadets, Company K-2, four years. Member of the 2008 National Champion Texas A\&M Fish Drill Team.}

    \resitem{Planned and executed an outfit reunion and Parent's Weekend banquet for +150 people with very limited assistance from underclassmen and peers.}

    \resitem{Member of TAULUG - Texas A\&M UNIX Linux Users Group.}

    \resitem{Amateur Radio Operator - KF5MWZ, General Class.}

    \resitem{Helped execute CCDC - Collegiate Cyber Defense Competition - as a member of the planning and execution "Gold Team".}

\end{ressection}


\end{document}

